Count and compile classifications

### 2021-06-17 analysis/step4_get_features_and_classifications/2_run_classsificatinos/count_classification_outputs.Rmd
for merging individual machine classifications

## Check we have values for all images
```{r}
library(tidyverse)
current_dir <- "classification-outputs-092020_C_0.1"
files <- dir(current_dir)
indexes = array()
count=0
for (f in files){
  count = count +1
  this_csv = read.csv(paste0(current_dir,'/',f)) 
  indexes[count] = this_csv$index
}
```

@@

```{r}
write.csv(all_data, paste0('compiled_classifications/Classification_Outputs',count,'.csv'))

>>>>

## Check we have values for all images
```{r}
library(tidyverse)
library(here)

```{r}
current_dir <- here::here("data/compiled/classification-outputs-062021_C_0.1/")

files = dir(current_dir)
indexes = array()
count=0
for (f in files){
  count = count +1
  this_csv = read.csv(paste0(current_dir,'/',f)) 
  indexes[count] = this_csv$index
}
```

@@

```{r}
write.csv(all_data, here::here("data/compiled/", paste0('compiled_classifications/Classification_Outputs',count,'.csv')))
